Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-05-16 TABLE/magnifications2.tex
more tweaks to discussion section. Updated some figs

\tablecaption{\changeR{Tested lens models for Abell 2744.\label{tab:LensModels}}}

@@

@@

Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{m} models for galaxy mass.\\
Diego\tablenotemark{n} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.

@@

\begin{deluxetable}{p{0.62in}ccc}
\tablecolumns{4}
\tablecaption{\changeR{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}}
\tablehead{ \colhead{Model\tablenotemark{a}} & 
            \colhead{Best\tablenotemark{b}} & \colhead{Median\tablenotemark{c}} & 
            \colhead{68\% Conf. Range\tablenotemark{d}}}
\startdata
Sharon(v1)      & 2.56     & 2.60  &   2.44$-$2.78 \\
Sharon(v2)      & 2.74     & 2.59  &   2.42$-$2.85 \\
CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
CATS(v2)        & \nodata  & 3.42  &   3.27$-$3.58 \\
GLAFIC          & 2.34     & 2.29  &   2.19$-$2.37 \\
Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\
Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\
Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28 \\
Diego$^{\rm *}$ &  \nodata  & 1.80  &   1.44$-$2.16 \\
\enddata
\tablenotetext{a}{Models marked by an asterisk were not part of the blind test, as they include modifications made after the measured magnification of the SN was known.}  
\tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{c}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
\tablenotetext{d}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
\end{deluxetable}

>>>>

\tablecaption{Tested lens models for Abell 2744.\label{tab:LensModels}}

@@

\cutinhead{Post-HFF models : include data from the HFF program}\\
Diego\tablenotemark{n} & 15 &  48 & 4 & 11  & \citealt{Diego:2014b} & Alternative implementation of the {\tt WSLAP+} model, using a different set of strong-lensing constraints and redshifts.\\
\cutinhead{Unblind models : generated after the SN magnification was known}\\

@@

Lam(v2)        & 10 &  32 & 5 & 5  &  \citealt{Lam:2014} & Updated version of the {\tt WSLAP+} model, using more selective strong-lensing constraints and GALFIT\tablenotemark{m} models for galaxy mass.

@@

\begin{deluxetable}{p{0.62in}ccc}
\tablecolumns{4}
\tablecaption{Lens model predictions for SN \tomas\ magnification\label{tab:PredictedMagnifications}}
\tablehead{ \colhead{Model\tablenotemark{a}} & 
            \colhead{Best\tablenotemark{b}} & \colhead{Median\tablenotemark{c}} & 
            \colhead{68\% Conf. Range\tablenotemark{d}}}
\startdata
Bradac(v1)      & 3.19     & 2.48  &   2.31$-$2.66 \\
CATS(v1)        & 2.28     & 2.29  &   2.25$-$2.34 \\
CATS(v1sw)      & \nodata  & 2.62  &   2.44$-$2.80 \\
Merten          & 2.33     & 2.24  &   2.04$-$2.92 \\
Sharon(v1)      & 2.56     & 2.60  &   2.44$-$2.78 \\
Sharon(v2)      & 2.74     & 2.59  &   2.42$-$2.85 \\
Zitrin-LTM      & 2.67     & 2.99  &   2.61$-$3.77 \\
Zitrin-NFW      & 2.09     & 2.29  &   2.07$-$2.52 \\
Williams        & 2.70     & 2.81  &   1.65$-$5.54 \\[0.1em]
\tableline\\[-0.5em]
CATS(v2)        & \nodata  & 3.42  &   3.27$-$3.58 \\
Diego           &  \nodata  & 1.80  &   1.44$-$2.16 \\
GLAFIC          & 2.34     & 2.29  &   2.19$-$2.37 \\
Lam(v1)         & \nodata  & 2.79  &   2.42$-$3.16 \\[0.5em]
Bradac(v2)$^{\rm *}$ & 2.23     & 2.26  &   2.30$-$2.23 \\
Lam(v2)$^{\rm *}$ & 1.86     & 1.91  &   1.54$-$2.28
\enddata
\tablenotetext{a}{Models above the line are from the pre-HFF set, and those below incorporate HFF data. The final two, marked by an asterisk, were not part of the blind test as they include modifications made after the measured magnification of the SN was known.}  
\tablenotetext{b}{The magnification returned for the optimal version of each model, as independently defined by each lens modeling team.}  
\tablenotetext{c}{Median magnification from 100-600 Monte Carlo realizations of the model.}  
\tablenotetext{d}{Confidence ranges about the median, enclosing 68\%\ of the realized values.}
\end{deluxetable}
